Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2025-01-10 paper/main.tex
minor updates to fig 6 results and methods

\begin{equation}
    \mathrm{ncorr}(x, y) = \frac{\mathrm{corr}(x, y) - \mathrm{mincorr}}{\mathrm{maxcorr} - \mathrm{mincorr}},
\end{equation}
and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
correlations between any lecture timepoint and question, taken over all
timepoints in the given lecture, and all five questions \textit{about} that lecture appearing on the given quiz.
We also define $f(s, \Omega)$ as the
$s$\textsuperscript{th} topic vector from the set of topic vectors $\Omega$.
Here $t$ indexes the set of lecture topic vectors, $L$, and $i$ and $j$ index
the topic vectors of questions used to estimate the knowledge trace, $Q$. Note
that ``correct'' denotes the set of indices of the questions the participant
answered correctly on the given quiz.

Intuitively, $\mathrm{ncorr}(x, y)$ is the correlation between two topic
vectors (e.g., the topic vector from one timepoint in a lecture, $x$, and the
topic vector for one question, $y$), normalized by the minimum and maximum
correlations (across all timepoints $t$ and questions $Q$) to range between 0
and 1, inclusive. Equation~\ref{eqn:prop} then computes the weighted average
proportion of correctly answered questions about the content presented at
timepoint $t$, where the weights are given by the normalized correlations
between timepoint $t$'s topic vector and the topic vectors for each question.
The normalization step (i.e., using $\mathrm{ncorr}$ instead of the raw
correlations) ensures that every question contributes some non-negative amount
to the knowledge estimate.

>>>>

\begin{equation}
    \mathrm{ncorr}(x, y) = \frac{\mathrm{corr}(x, y) - \mathrm{mincorr}}{\mathrm{maxcorr} - \mathrm{mincorr}},
\end{equation}
and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
correlations between any lecture timepoint and question, taken over all
timepoints in the given lecture, and all five questions \textit{about} that
lecture appearing on the given quiz. We also define $f(s, \Omega)$ as the
$s$\textsuperscript{th} topic vector from the set of topic vectors $\Omega$.
Here $t$ indexes the set of lecture topic vectors $L$, and $i$ and $j$ index
the topic vectors of questions $Q$ used to estimate the knowledge trace. Note
that ``correct'' denotes the set of indices of the questions the participant
answered correctly on the given quiz.

Intuitively, $\mathrm{ncorr}(x, y)$ is the correlation between two topic
vectors (e.g., the topic vector $x$ for one timepoint in a lecture and the
topic vector $y$ for one question), normalized by the minimum and maximum
correlations (across all timepoints $t$ and questions $j$) to range between 0
and 1, inclusive. Equation~\ref{eqn:prop} then computes the weighted average
proportion of correctly answered questions about the content presented at
timepoint $t$, where the weights are given by the normalized correlations
between timepoint $t$'s topic vector and the topic vectors for each question.
The normalization step (i.e., using $\mathrm{ncorr}$ instead of the raw
correlations) ensures that every question contributes some non-negative amount
to the knowledge estimate.
